A Plasma Torus Around a Young Low-Mass Star

### 2025-04-03 paper/ms.tex
update

\begin{figure}[!tp]
  \centering
  \includegraphics[width=0.5\textwidth]{figures/sf6.pdf}
  \caption{Time-variable fit to H$\alpha$ line profiles.
  {\it Left column:} Raw spectrum at each epoch $f_{\lambda}$ minus
  the time-averaged spectrum $f_{\langle t \rangle}$ (as in
  Figure~\ref{fig:spec}e).
  Underplotted sinusoids are to guide the eye.
  {\it Middle columns:} Model of emission from the inner clump (sum of
  two gaussians) and the outer clump (single gaussian), plotted over
  the data.
  {\it Right column:} Residual of the left column after subtracting
  the sum of the two middle columns, leaving variability in the line
  core.  
  Section~\ref{subsec:halpha} discusses the use of this model.
  }
  \label{fig:halphamodel}
\end{figure}

@@

Caution is required in the interpretation of this model's results.
The model at times overfits, because it targets the most significant
spectral feature around the priors discussed above, and sometimes
these features are not statistically significant.  During such
spectral epochs, e.g.~the ``outer'' clump at $\phi$=1.07, the model is
fitting noise, not signal.  
At times the model underfits.  For instance, the sudden blue rise near
$\phi$=0.2 is not well-matched by the functional form of a gaussian;
the assumed functional form is one of convenience.
A final point of caution is that the model fits the $i=\{ 0, 1 \}$,
and $i=2$ components independently.  At $\phi=0.0$ and $1.0$,
Figure~\ref{fig:halphamodel} suggests that this means the emission might
hypothetically be from either the inner or outer components.  A
physical interpretation however is that this is the phase during which
the inner component is in transit, and the outer is in secondary
occultation and blocked by the star.  At $\phi=0.0$, the double-peaked
emission profile also matches that seen shortly afterward when the
inner clump is viewed off-disk.  A physical interpretation of the
model should therefore discard the results at this particular epoch
for the outer clump.

Taking these caveats into account, the results from Extended Data
Table~\ref{tab:halphamodelparams} can be used to evaluate various
models for the orbits.

, and in particular to assess their periods and
semi-amplitudes.

>>>>

\begin{figure}[!tp]
  \centering
  \includegraphics[width=0.5\textwidth]{figures/sf6.pdf}
  \caption{Time-variable fit to H$\alpha$ line profiles.
  {\it Left column:} Raw spectrum at each epoch $f_{\lambda}$ minus
  the time-averaged spectrum $f_{\langle t \rangle}$ (as in
  Figure~\ref{fig:spec}e).
  Underplotted sinusoids are not fits; they are meant to guide the eye.
  {\it Middle columns:} Model of emission from the inner clump (sum of
  two gaussians) and the outer clump (single gaussian), plotted over
  the data.
  {\it Right column:} Residual of the left column after subtracting
  the sum of the two middle columns, leaving variability in the line
  core.  
  Section~\ref{subsec:halpha} discusses the use of this model.
  }
  \label{fig:halphamodel}
\end{figure}

@@

Caution is required in the interpretation of this model's results.
The model at times overfits, because it targets the most significant
spectral feature around each component's prior, and sometimes these
features are not statistically significant.  During such spectral
epochs, e.g.~the ``outer'' clump at $\phi$=1.07, the model fits noise,
not signal.  At other times, the model underfits.  For instance, the
sudden blue rise near $\phi$=0.2 is not well-described by the
functional form of a gaussian; the assumed functional form is one of
convenience.  A final point of caution is that the model fits the
$i=\{ 0, 1 \}$, and $i=2$ components independently.  At $\phi=0.0$ and
$1.0$, Figure~\ref{fig:halphamodel} suggests that this means the
emission might hypothetically be from either the inner or outer
components.  A physical interpretation however is that this is the
phase during which the inner component is in transit, and the outer is
in secondary occultation and blocked by the star.  At $\phi=0.0$, the
double-peaked emission profile also matches that seen shortly
afterward when the inner clump is viewed off-disk.  A physical
interpretation of the model should therefore discard the results at
this particular epoch for the outer clump.

\begin{figure}[!tp]
  \centering
  \includegraphics[width=0.4\textwidth]{figures/sf7.pdf}
  \caption{Example orbits fit to velocities extracted from gaussian
  profile fits in Figure~\ref{fig:halphamodel}.
  Each marker represents the measured best-fit mean and its best-fit
  standard deviation at a given epoch.
  Solid circles were used in the sinusoidal fits; transparent X markers
  were excluded due to various concerns about their epoch-by-epoch
  interpretation (see text).  The main purpose of this exercise was to
  quantify the orbital periods and semi-amplitudes of the
  circumstellar clumps.  The inner double-peaked clump is shown in
  orange blue; the outer clump is shown in green.}
  \label{fig:orbits}
\end{figure}

Taking these caveats into account, we used the results from Extended
Data Table~\ref{tab:halphamodelparams} to evaluate various models for
the orbits.
Our main goal in this exercise was to quantify the orbital periods,
velocities, and velocity dispersions of these clumps.
Figure~\ref{fig:orbitmodel} shows some representative results for the
circular orbit case.
For
